### 2023-01-31 manuscript.tex
FDO citations [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/36d2cc87aca77995c39b6fea4ee9a6aa69587b8e.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/36d2cc87aca77995c39b6fea4ee9a6aa69587b8e/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4056315166

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/8bbdd67883c9ed6306479264d368472288bd67d0/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/8bbdd67883c9ed6306479264d368472288bd67d0}{stain/2022-fdo-paper@8bbdd67}
on January 31, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/36d2cc87aca77995c39b6fea4ee9a6aa69587b8e/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/36d2cc87aca77995c39b6fea4ee9a6aa69587b8e}{stain/2022-fdo-paper@36d2cc8}
on January 31, 2023.
